Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-21 prop_letter.tex
prop_letter.tex \newcommand{\yutsung}[1] Fix the width for two-column paper...

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

In order to model the idea of finite precision measurement, we replace
the range of $\mu$ from the infinity precision~$[0,1]$ to a collection
of finite number of intervals~$\mathscr{I}$, and consider a quantum
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. It is intuitive
to consider $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
and 
\begin{equation}
[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
\end{equation}
 so that $\bar{\mu}$ satisfy
 \begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion. This becomes intuitive if we compare each terms in two
sides of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}).
Although we have $\mathbb{1}=\left(\mathbb{1}-P\right)+P$, but when
$r>l$, the left-hand side~$\bar{\mu}(\mathbb{1})=\left[1,1\right]$
is a proper subset of the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$.
Then, Gleason's theorem can be expressed as the limit case when the
collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
In the next paragraph, we will show the Kochen-Specker theorem is
another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\Tr}{\mathop{\mathrm{Tr}}\nolimits}

@@

In order to model the idea of finite precision measurement, we replace
the range of $\mu$ from the infinity precision~$[0,1]$ to a collection
of finite number of intervals~$\mathscr{I}$, and consider a quantum
IVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$. It is intuitive
to consider $\left[0,0\right]$, $\left[1,1\right]\in\mathscr{I}$
and to define $\left[1,1\right]-\left[l,r\right]=\left[1-r,1-l\right]$
and 
\begin{equation}
[l_{1},r_{1}]+[l_{2},r_{2}]=[l_{1}+l_{2},r_{1}+r_{2}]
\end{equation}
 so that $\bar{\mu}$ satisfy
 \begin{itemize}
\item $\bar{\mu}(\mathbb{0})=\left[0,0\right]$. 
\item $\bar{\mu}(\mathbb{1})=\left[1,1\right]$. 
\item For any projection $P$, 
\begin{equation}
\bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Complement}
\end{equation}
\item For a set of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have 
\begin{equation}
\bar{\mu}\left(\sum_{i=1}^{N}P_{i}\right)\subseteq\sum_{i=1}^{N}\bar{\mu}\left(P_{i}\right)\textrm{ .}\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{itemize}
Notice that Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
relaxes the equality in Eq.~(\ref{eq:QuantumProbability-Addition})
to inclusion. This becomes intuitive if we compare each terms in two
sides of Eq.~(\ref{eq:QuantumInterval-valuedProbability-Complement}).
Although we have $\mathbb{1}=\left(\mathbb{1}-P\right)+P$, but when
$r>l$, the left-hand side~$\bar{\mu}(\mathbb{1})=\left[1,1\right]$
is a proper subset of the right-hand side~$\bar{\mu}\left(\mathbb{1}-P\right)+\bar{\mu}\left(P\right)=\left[1+l-r,1+r-l\right]$.
\yutsung{We use a section to motivate and introduce classical IVPMs.
How to use classical IVPMs to justify quantum IVPMs without interrupting
the flow?}\\
Then, Gleason's theorem can be expressed as the limit case when the
collection of intervals are all singletons~$\mathscr{I}_{\infty}=\set{\left[x,x\right]}{x\in\left[0,1\right]}$.
In the next paragraph, we will show the Kochen-Specker theorem is
another limit case when the collection of intervals are $\mathscr{I}_{\mathrm{D}}=\left\{ \imposs,\necess\right\} $,
where $\imposs=\left[0,0\right]$ and $\necess=\left[1,1\right]$.\newpage{}
